\textbf{Introducing the Choice-Confidence (CHOCO) Model for Bimodal Scales Data: Application to the Relationship between Reality Beliefs about AI-Generated Faces and Beauty}

### 2025-05-29 paper/manuscript.qmd
updated manuscript

There were also modifications to the instructions provided to participants. 
In Phase 1, an additional prompt was introduced, stating that the study was conducted in partnership with a young AI startup. 
This was intended to strengthen participants’ belief that the faces they were shown could plausibly be either real or AI-generated. 
Additionally, participants were explicitly asked to respond based on their immediate, first impressions—an instruction not included in the first study.

>>>>

There were also modifications to the instructions provided to participants and in the paradigm. 
In Phase 1, an additional prompt was introduced, stating that the study was conducted in partnership with a young AI startup. 
This was intended to strengthen participants’ belief that the faces they were shown could plausibly be either real or AI-generated. In this phase, a prompt appeared for 1–2 seconds before each face, informing participants whether the upcoming image was "AI-generated" or "Photograph", notably, all faces were in fact real photograph.

### 2025-05-29 paper/manuscript.tex
updated manuscript

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Andy Field}{true}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, bottomrule=.15mm, colback=white, colframe=quarto-callout-note-color-frame, opacityback=0, breakable, arc=.35mm, leftrule=.75mm, toprule=.15mm, left=2mm]

@@

There were also modifications to the instructions provided to
participants. In Phase 1, an additional prompt was introduced, stating
that the study was conducted in partnership with a young AI startup.
This was intended to strengthen participants' belief that the faces they
were shown could plausibly be either real or AI-generated. Additionally,
participants were explicitly asked to respond based on their immediate,
first impressions---an instruction not included in the first study.

>>>>

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Andy Field}{true}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, arc=.35mm, left=2mm, colback=white, rightrule=.15mm, bottomrule=.15mm, leftrule=.75mm, breakable, toprule=.15mm, opacityback=0]

@@

There were also modifications to the instructions provided to
participants and in the paradigm. In Phase 1, an additional prompt was
introduced, stating that the study was conducted in partnership with a
young AI startup. This was intended to strengthen participants' belief
that the faces they were shown could plausibly be either real or
AI-generated. In this phase, a prompt appeared for 1--2 seconds before
each face, informing participants whether the upcoming image was
``AI-generated'' or ``Photograph'', notably, all faces were in fact real
photograph.
